\begin{list}{\scalebox{0.7}{$\square$}}{\leftmargin=1em \itemindent=0em}
	\item DUNE Collaboration, ``\textit{DUNE Phase-II: Scientific Opportunities, Detector Concepts, Technological Solutions}'', JINST \textbf{19}, 12, P12005 (2024).
	\item DUNE Firmware Readout Group, ``\textit{Firmware Trigger Primitive Generation in DUNE Data Acquisition System}'', DUNE Technical Note, DUNE-doc-29412 (2023).
	\item DUNE DAQ Project, ``\textit{Trigger and Data AcQuisition (TDAQ) System Design}'', DUNE-DAQ Design Review, EDMS-2826454 (2022). \newline
	%\item DUNE Collaboration, ``\textit{The track-length extension fitting algorithm for energy measurement of interacting particles in liquid argon TPCs and its performance with ProtoDUNE-SP data}'', arXiv:2409.18288 (2024).
	\item DUNE Collaboration, ``\textit{First measurement of the total inelastic cross section of positively charged kaons on argon at energies between 5.0 and 7.5 GeV}'', Phys.Rev.D \textbf{110}, 9, 092011 (2024).
	\item DUNE Collaboration, ``\textit{Performance of a modular ton-scale pixel-readout liquid argon time projection chamber}'', Instruments \textbf{8}, 3, 41 (2024).
	\item DUNE Collaboration, ``\textit{Doping Liquid Argon with Xenon in ProtoDUNE Single-Phase: Effects on Scintillation Light}'', JINST \textbf{19}, 08, P08005 (2024).
	\item DUNE Collaboration, ``\textit{Impact of cross-section uncertainties on supernova neutrino spectral parameter fitting in the Deep Underground Neutrino Experiment}'', Phys. Rev. D \textbf{107}, 11, 112012 (2023).
	%\item DUNE Collaboration, ``\textit{Highly-parallelized simulation of a pixelated LArTPC on a GPU}'', JINST \textbf{18}, 04, P04034 (2023).
	\item DUNE Collaboration, ``\textit{Identification and reconstruction of low-energy electrons in the ProtoDUNE-SP detector}'', Phys. Rev. D \textbf{107}, 9, 092012 (2023).
\end{list}

